Introducing statistics with \\texttt{intRo}

### 2014-12-11 student-paper-competition-2014/paper.Rmd
Incorporate scrimshaw paper

# Introduction
The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly been a great development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may be unfamiliar to the introductory statistics student. This issue may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors would tend to use a tool like \texttt{R} in their own work. Still, signficant compromises must be made when using software like \texttt{JMP}, including dealing with software licenses, unsupported desktop platforms, and non-ideal user interface decisions. In teaching STAT 226 at Iowa State University, we witnessed profound struggles by students attempting to practice the introductory concepts discussed in class. Often, these struggles were directly related to the use of the software and not any sort of fundamental misunderstanding of the material.

>>>>

# Introduction
The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly been a great development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may be unfamiliar to the introductory statistics student. This issue may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors would tend to use a tool like \texttt{R} in their own work. Still, signficant compromises must be made when using software like \texttt{JMP}, including dealing with software licenses, unsupported desktop platforms, and non-ideal user interface decisions.

In teaching STAT 226 at Iowa State University, we witnessed profound struggles by students attempting to practice the introductory concepts discussed in class. Scrimshaw notes in his manuscript that "open-ended packages, like any others, may create obstacles to learning simply through their lack of user-friendliness in the sheer mechanics of operating them, rather than any intrinsic difficulty in the content...." [@scrimshaw2001computers] In our own experience teaching, students' struggles were often directly related to the use of the software and not any sort of fundamental misunderstanding of the material, in agreement with Scrimshaw's finding.
